draft_final_assignment

### 2022-11-28 draft_final_assingment.Rmd
Update draft_final_assingment.Rmd

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_punct = TRUE, groups = corp$party) %>%
    dfm_trim(min_termfreq = 3)

@@

corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"), remove_punct = TRUE, groups = corp_115$party) %>% dfm_trim(min_termfreq = 3)

@@

corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_punct = TRUE, groups = corp_116$party) %>% dfm_trim(min_termfreq = 3)

@@

corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_punct = TRUE, groups = corp_117$party) %>% dfm_trim(min_termfreq = 3)

>>>>

dfmatRepDem <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
    dfm_trim(min_termfreq = 3)

@@

corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

corp_117 <- df %>% filter(session == 117) %>% rename(text = summary) %>% corpus()
modelpart17 <- dfm(corp_117, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_117$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)
